\subsection*{Concerns}
There have been a number of cluster meetings with the groups from Mathematics (MAT) and Internet Technologies and Computer Systems (ITC), and us, Computer Science (DAT), as well as with each group's project supervisors.
In the beginning there was a bit of uncertainty in our group about how the entire process would work, since each group in the cluster had a different curriculum and a different set of requirements to be fulfilled.
Furthermore, we were concerned about the fact that each group had to figure out a part of the whole solution based on the work of others.
Essentially, it sounded like MAT would develop an algorithm as a base for us (the Computer Science group) to use.
DAT would then use this algorithm and develop a class library for the ITC group to use.
ITC would finally use the algorithm and the library in their project.
This would require a lot of time and be largely inefficient, since one step of the process had to be completed before another one could begin, and we only had about four months for the project in total.
It would also mean that ITC would be dependant on DAT, while DAT would be dependant on MAT for their respective projects, and that would not be feasible.
In a similar vein, the point of the cluster group was that each group could benefit from the work of others.
But how could our group benefit from the work of ITC if they were dependant on us? And would MAT gain any benefit from the cluster group at all?

We brought these concerns to the table at the first cluster meeting with each group's advisor and Hans Hüttel, who made the project proposal.

\subsection*{Trying to work together}
There was no real progress in the cluster collaboration during the first weeks, which was expected, as we were all finding out which direction we wanted to take..
Everyone was busy learning about steganography and how to use it.
Our group made a fairly trivial programme to embed data into other data using least significant bits, but we could not spend the entire project on that. However, this programme was not completely useless with regards to ITC, as ITC could use it, and it was decided that DAT would deliver either that or whichever better programme that was developed later.

Olav Geil, MAT's advisor, held a lecture on an article about a graph-theoretic approach to steganography\citep{hetzl_2005}.
This proved to be valuable to both us and MAT, as both groups would later decide to use this approach in some form.
DAT and MAT somewhat connected over this, thinking this could be the key to the lacking collaboration.
We were encouraged by the supervisors to collaborate, perhaps letting MAT develop and giving us an efficient algorithm using this approach, while DAT developed a slightly less efficient algorithm for testing purposes until MAT was done with their investigations.
When voicing concern about how MAT would benefit from this, we were told that it could possibly be exciting for them to see their algorithm in action.

To solidify the demise of the cluster project, we realised at a cluster meeting - roughly a month before the final deadline - that DAT and MAT had chosen different paths.
MAT had dedicated their time to make the algorithm presented by Olav Geil as precise as possible, sacrificing efficiency, while DAT were looking for an efficient algorithm where extreme precision had less of a priority.
This meant that MAT and DAT would be of no use to each other, and it was decided that it was the end of the collaboration between DAT and MAT.
ITC will still get a complete steganographic solution to use as a library with select methods exposed, since they will have no use of the entire codebase in their project.
