\documentclass[a4paper,12pt,hidelinks]{article}
\usepackage[pdftex]{graphicx} 
\usepackage{type1cm}
\usepackage{a4}
\usepackage{lastpage}
\input{preamble.tex}
\usepackage[ddmmyyyy]{datetime}

\newcommand{\group}{A4-423}

\setcounter{secnumdepth}{4}

\begin{document}
	\title{Group Contract}
	\author{\group}
	\maketitle
	
	These are the points group A4-423 have come to agreement on. If any changes are to be made, the majority of the group must agree on them.
	\begin{itemize}
		\item We have decided to use the following tools and technologies in this project:
		\begin{description}
			\item[Trello] for short term planning. It will be used for keeping track of what needs to be done, and what is already in progress.
			\item[Git] for version control of all files. We will use GitHub for hosting our project, both our worksheets and program source files. This will guarantee that all group members have full access to all files.
			\item[Slack] for all online communication in the group. This is also where we will share information we find online, so that all members of the group can read the literature before a group meeting. 
		\end{description}
		\item We will have a scheduled meeting every Thursday at 09.00. On this meeting we will decide how to progress with the project in the following week. This is also where we will decide when we need to show up in the group room until the next scheduled meeting.
		\item In the group, we require an attendance rate of 80\%, if that is not the case, the group will discuss the absence at a meeting, and how to progress from there. If the attendance rate falls below 65\%, the member will be removed from the group.
		\item At every other meeting, a project manager will be chosen, and will be the one follows up on worksheets, and makes sure that work is being done by all members. The role will take turns, so that all members try it at least one.
		\item We require all members of the group to be active in their studies. All members are required to show up to lectures and the following group activities.
		\item All sources used in worksheets are to be added to the global file of sources used by the group. Sources must be added while writing the work sheets, and not after the work sheet is done. 
		\item All websites used as sources must be downloaded in PDF-format and be given a reasonable name so that the source can be easily located at a later point.
		\item All work sheets must be corrected by another group member, to keep all work similar in writing style.
		\item Jakob, Jacob, Leo, Mathias and Henrik have each given an equal sum of money towards the deposit for the keys to our grouproom door. Everyone has one key except Henrik, who has two.
	\end{itemize}

	\begin{itemize}
		\item 24 hours before a scheduled meeting with our supervisor, an agenda and work sheets will be sent to the supervisor, so that he has time to prepare for our questions, and read the work sheets.
	\end{itemize}
	\section*{Handling of Conflicts}
	If there are problems with one member of the group, another member of the group will talk to that person about the issues the other members of the group have experienced. In this way, the discussion will not come across as intimidating. The member who begins the discussion will be the project manager of that week.
\end{document} 